Title

### 2013-03-21 inc/gun/gun_design.tex
tweak gun design intro now that design considerations presents the argument for large area emission

The acceleration region of our prototype UEM system has several requirement which are unique in comparison to standard electron guns.
Primarily, given the limitations on the beam discussed earlier, %TODO link to discussion of Childs law beam size limitation
the employ laser pulse must be a relatively large area.
This concern leads to several additional criteria.
To accomodate this large beam, the anode aperture must be similarly large; in fact, this will be larger than the emission source due to beam expansion during acceleration.
Also, in transit from the cathode to the anode, this large beam is more susceptable to non-uniformities in the accelerating electic field given that it will span a wider proportion of the accelerator than thin beams used in standard TEM.

>>>>

The acceleration region of our prototype UEM system has several requirement which are unique in comparison to standard electron guns.
As discussed in \ref{chap:considerations} notable requirements include the need to handle a large photoemission area and the inability to employ a pin-hole to selectively clean the electron beam.
This concern leads to several additional criteria.
The system must first be able to accept the large laser spot size needed to generate the electron beam.
Then, in order to accomodate this large electron pulse, both the cathode Wehnelt and anode aperture must be similarly large; in fact, the beam size at the anode aperture will typically be larger than at the emission source due to beam expansion during acceleration.
Also, care must be taken to ensure a relatively uniform electric field for acceleration of the pulse.
While in transit from the cathode to the anode, this large beam is more susceptable to non-uniformities in the electic field given that it will span a wider proportion of the accelerator than the thin beams used in conventional TEM.
